---
title: "Regresion Logistica"
author: "Pavel"
date: "5 de abril de 2020"
output:
  word_document:
    reference_docx: templateStyles.docx
---

# Logistic Regression

```{r tidy=TRUE, include=FALSE}
confidence<-NA
datos.entreno.alg<-datos.entreno
datos.test.alg<-datos.test
```


__Logistic Regression algorithm needs the target variable to be numeric__
```{r tidy=TRUE}

datos.entreno.alg[[var_diagnosis]]<-as.factor(datos.entreno.alg[[var_diagnosis]])
datos.test.alg[[var_diagnosis]]<-as.factor(datos.test.alg[[var_diagnosis]])

datos.entreno.alg[[var_diagnosis]]<-as.numeric(datos.entreno.alg[[var_diagnosis]])
datos.test.alg[[var_diagnosis]]<-as.numeric(datos.test.alg[[var_diagnosis]])
```
\vspace{10mm}

__Logistic Regression algorithm uses only dichotomus variable as target variable. So in fuction of the patient, it will be adjusted in order just to get two possible values 1/0__
\vspace{3mm}

```{r tidy=TRUE, include=FALSE}
if (paciente=="MAPI"){
  # Solo evaluaremos si el estado es No Hipomanía(0) o Hypomania (1)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==1,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==1,1,0)
} else if (paciente=="ECSA"){
  # Solo evaluaremos si el estado es Euthymia(0) o Hypomania (1)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==1,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==1,1,0)
} else if (paciente=="DOSI"){
  # Solo evaluaremos si el estado es Depresion(1) o No Depresion (0)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==-1,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==-1,1,0)
} else if (paciente=="CASGA"){
  #Solo evaluaremos si el estado es Hipomanía (1) o Mixed (0)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==1,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==1,1,0) 
} else if (paciente=="GIUS"){
  # Solo evaluaremos si el estado es deprimido. Depression (1) , resto(0)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==-1,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==-1,1,0)  
} else if (paciente=="SAPE"){
  # Solo evaluaremos si el estado es Euthymia (0) o Hypomania (1)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==1,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==1,1,0)
} else if (paciente=="ALPA"){
  # Solo evaluaremos si el estado es Mixed (1) o Euthymia (0)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==2,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==2,1,0)
} else if (paciente=="DOGE"){
  # Solo evaluaremos si el estado es Mixed (1) o Euthymia (0)
  datos.entreno.alg[[var_diagnosis]]<-ifelse(datos.entreno.alg[[var_diagnosis]]==2,1,0)
  datos.test.alg[[var_diagnosis]]<-ifelse(datos.test.alg[[var_diagnosis]]==2,1,0)
}
```
\vspace{10mm}

__Creating model__
```{r tidy=TRUE}
formula<-as.formula(paste0(var_diagnosis,"~."))
(modelo_glm<-glm(formula,data=datos.entreno.alg,family=binomial))
```
\vspace{10mm}

__Variable importance__
```{r tidy=TRUE}
vimp<-as.data.frame(modelo_glm$coefficients)
vimp[order(vimp$`modelo_glm$coefficients`),,drop=FALSE]
```
\vspace{10mm}


__Performing predictions__
```{r tidy=TRUE}
options(scipen=999)
predicciones <- predict(modelo_glm, datos.test.alg,type="response")
predicciones
```
\vspace{10mm}

__For comparison purposses, predictios are added to test dataset__
```{r tidy=TRUE}
datos.test.alg$prediccion_glm <- predicciones
realvspredict<-datos.test.alg[,c(var_diagnosis,"prediccion_glm")]
realvspredict
```
\vspace{10mm}

__Rouding predictions__
```{r tidy=TRUE}
realvspredict$prediccion_glm<-round(realvspredict$prediccion_glm)
realvspredict$correct<-ifelse(realvspredict$prediccion_glm==realvspredict[[var_diagnosis]],"YES","NO")
realvspredict
```
\vspace{10mm}

__Confidence__
```{r tidy=TRUE}
confidence<-(nrow(realvspredict[realvspredict$correct=="YES",])/nrow(realvspredict))*100
confidence
```
\vspace{10mm}

```{r include=FALSE}
if (ind_ml=="ALL") {
dfconfidence1[dfconfidence1$patients==paciente,c("log_reg")]<-confidence
dfvar1<-rbind(dfvar1,data.frame(patient=pt,algorithm="log_reg",variables=ncol(datos.entreno.alg),obs.train=nrow(datos.entreno.alg),obs.test=nrow(datos.test.alg),states=paste(unique(datos.entreno$E_diagnosis),collapse=",")))
} else {
dfconfidence2[dfconfidence2$patients==paciente,c("log_reg")]<-confidence
dfvar2<-rbind(dfvar2,data.frame(patient=pt,algorithm="log_reg",variables=ncol(datos.entreno.alg),obs.train=nrow(datos.entreno.alg),obs.test=nrow(datos.test.alg),states=paste(unique(datos.entreno$E_diagnosis),collapse=",")))
}
```
\vspace{10mm}

\pagebreak
