---
title: "rf"
author: "Pavel"
date: "22 de marzo de 2020"
output:
  word_document:
    reference_docx: templateStyles.docx
---

# Random Forest Model (all variables)

```{r tidy=TRUE, include=FALSE}
confidence<-NA
datos.entreno.alg<-datos.entreno
datos.test.alg<-datos.test
```
__Random Forest algorithm needs the target variable to be factor__
```{r tidy=TRUE}
datos.entreno.alg[[var_diagnosis]]<-as.factor(datos.entreno.alg[[var_diagnosis]])
datos.test.alg[[var_diagnosis]]<-as.factor(datos.test.alg[[var_diagnosis]])
```

__Creating model__
\vspace{10mm}
```{r tidy=TRUE}
formula<-as.formula(paste0(var_diagnosis,"~."))
(modelo_rf<-randomForest(formula,data=datos.entreno.alg))
```
\vspace{10mm}
  
__Variables importance__
\vspace{10mm}
```{r tidy=TRUE}
vimp<-as.data.frame(modelo_rf$importance)
vimp[order(vimp$MeanDecreaseGini),,drop=FALSE]
```
\vspace{10mm}

__Performing predictions__
\vspace{10mm}
```{r tidy=TRUE}
predicciones <- predict(modelo_rf, datos.test.alg)
predicciones
```
\vspace{10mm}

__Confusion matrix__
\vspace{10mm}
```{r tidy=TRUE}
(mc<-table(predicciones,datos.test.alg[[var_diagnosis]]))
```
\vspace{10mm}

__Confidence__
\vspace{10mm}
```{r tidy=TRUE}
confidence<-100 * sum(diag(mc)) / sum(mc)
confidence
```

```{r include=FALSE}

if (ind_ml=="ALL") {
dfconfidence1[dfconfidence1$patients==paciente,c("rf_all")]<-confidence
dfvar1<-rbind(dfvar1,data.frame(patient=pt,algorithm="rf_all",variables=ncol(datos.entreno.alg),obs.train=nrow(datos.entreno.alg),obs.test=nrow(datos.test.alg),states=paste(unique(datos.entreno.alg$E_diagnosis),collapse=",")))
} else {
dfconfidence2[dfconfidence2$patients==paciente,c("rf_all")]<-confidence
dfvar2<-rbind(dfvar2,data.frame(patient=pt,algorithm="rf_all",variables=ncol(datos.entreno.alg),obs.train=nrow(datos.entreno.alg),obs.test=nrow(datos.test.alg),states=paste(unique(datos.entreno.alg$E_diagnosis),collapse=",")))  
  
}
```
\pagebreak

# RANDOM FOREST (no caffeine)
__Removing caffeine variable__
\vspace{10mm}
```{r tidy=TRUE}
confidence<-NA
datos.entreno.alg.sc<-datos.entreno.alg [,!colnames(datos.entreno.alg)=='D_caffeine']
datos.test.alg.sc<-datos.test.alg [,!colnames(datos.test.alg)=='D_caffeine']
names(datos.entreno.alg.sc)
```
\vspace{10mm}

__Creating model__
\vspace{10mm}
```{r tidy=TRUE}
(modelo_rf<-randomForest(formula,data=datos.entreno.alg.sc))
```
\vspace{10mm}

__Variables importance__
\vspace{10mm}
```{r tidy=TRUE}
vimp<-as.data.frame(modelo_rf$importance)
vimp[order(vimp$MeanDecreaseGini),,drop=FALSE]
```
\vspace{10mm}

__Performing predictions__
```{r tidy=TRUE}
predicciones <- predict(modelo_rf, datos.test.alg.sc)
predicciones
```
\vspace{10mm}

__Confusion matrix__
```{r tidy=TRUE}
(mc<-table(predicciones,datos.test.alg[[var_diagnosis]]))
```
\vspace{10mm}

__Confidence__
```{r tidy=TRUE}
confidence<-100 * sum(diag(mc)) / sum(mc)
confidence
```

```{r include=FALSE}

if (ind_ml=="ALL") {
  dfconfidence1[dfconfidence1$patients==paciente,c("rf_no_caffeine")]<-confidence
  dfvar1<-rbind(dfvar1,data.frame(patient=pt,algorithm="rf_no_caffeine",variables=ncol(datos.entreno.alg.sc),obs.train=nrow(datos.entreno.alg.sc),obs.test=nrow(datos.test.alg.sc),states=paste(unique(datos.entreno.alg.sc$E_diagnosis),collapse=",")))
  
} else {
  dfconfidence2[dfconfidence2$patients==paciente,c("rf_no_caffeine")]<-confidence
  dfvar2<-rbind(dfvar2,data.frame(patient=pt,algorithm="rf_no_caffeine",variables=ncol(datos.entreno.alg.sc),obs.train=nrow(datos.entreno.alg.sc),obs.test=nrow(datos.test.alg.sc),states=paste(unique(datos.entreno.alg.sc$E_diagnosis),collapse=",")))  
  
}
```
\pagebreak
